---
title: "Exercise03-Missing_Data"
author: "Ken Suzuki"
date: "2023-10-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

A researcher is interested in predicting depression from trait anxiety and agreeableness. The dataset is called epi.bfi and resides within the psychTools package.

Depression was measured with the Beck Depression Inventory (bdi), trait anxiety was measured with the State-Trait Anxiety Inventory (traitanx), and agreeableness was measured with the Big 5 Inventory (bfagree). Use α = .05 for any null hypothesis testing.

```{r}
#Load required libraries
library(psychTools)
library(missMethods)

# Load and check the dataset
d <- epi.bfi
str(d)
head(d)
nrow(d) #This is to find out the number of rows (data pints) in the dataset

```

```         
Variable Descriptions
epiE: EPI Extraversion
epiS: EPI Sociability (a subset of Extraversion items
epiImp: EPI Impulsivity (a subset of Extraversion items
epilie: EPI Lie scale
epiNeur: EPI neuroticism
bfagree: Big 5 inventory (from the IPIP) measure of Agreeableness
bfcon: Big 5 Conscientiousness
bfext: Big 5 Extraversion
bfneur: Big 5 Neuroticism
bfopen: Big 5 Openness
bdi: Beck Depression scale
traitanx: Trait Anxiety
stateanx: State Anxiety
```

------------------------------------------------------------------------

### Full Model

#### **Review Full model (without deletion) [a]. Use the delete_MCAR function from the missMethods package to randomly remove 15% of cases from each variable. Save this dataset with a new name [].**

#### Review the FULL Model

```{r}
# Run a full model without removing any data points for a comparison purposes.

complete_m <- lm(bdi ~ traitanx + bfagree, data = d)
summary(complete_m)
confint(complete_m)

# Extract and save coefficients, SEs and p-values as "Values" for the comparison later (See b4).
(coeffs<-summary(complete_m)$coefficients[,"Estimate"]) 
(stderrs<-summary(complete_m)$coefficients[,"Std. Error"])
(pvals<-summary(complete_m)$coefficients[,"Pr(>|t|)"])
```

------------------------------------------------------------------------

### Deletion

##### Conduct List-wise Deletion

```{r}
library(missMethods)

# Randomly remove 15% of data points and store it as likewise_15
listwise_15 <- delete_MCAR(ds = d, p = .15)
(colMeans(is.na(listwise_15)))*100 

#The above is showing what proportion of the data is missing. 15.15152 means it is missing just over 15% of data.
```

#### Determine if the missing data can be classified as 'missing completely at random' (you should be able to predict the answer from Q1).

```{r}
library(naniar)
mcar_test(listwise_15)
```

#### ***Conclusion: The non-significant p.value = 0.467 suggests that the missing data is likely missing completely at random.*** 

------------------------------------------------------------------------

### Run GLM

#### 3) Run a general linear model predicting depression from trait anxiety and agreeableness using each of the following strategies:

```{r}
listwise_m <- lm(bdi ~ traitanx + bfagree, data = listwise_15)
summary(listwise_m)
confint(listwise_m)
```

**Note. The deletion of missingness for lm() is LISTWISE deletion as a default. They take out the data point entirely.**

------------------------------------------------------------------------

#### Compare Between Full Model and Listwise Deletion using rbind()

```{r}
# Compare the coefficients between Original model and Listwise Model
(coeffs <- rbind(coeffs, coef(listwise_m))) # rbind(First item, Second item(model))

# Compare the SDs between Original model and Listwise Model
(SEs =  rbind(stderrs, summary(listwise_m)$coefficients[,"Std. Error"]))

# Compare the p.values between the two models
(pvals<-rbind(pvals,summary(listwise_m)$coefficients[,"Pr(>|t|)"]))
```

**Note. The Full model (First row) compared to the Listwise model (Second row)**

------------------------------------------------------------------------

### Imputations:

##### Regression Imputation

mice: "norm.predict" and m = 1 is Regression Imputation

```{r}
# Load mice package for Regressioni Imputation
library(mice)

# Impute Listwise data (listwise_m) with Regression imputation (use method = norm.predict)
Listwise_m_Reg_Imputation <- mice(listwise_15, method = "norm.predict", m = 1) # m = 1 is how many times you want to run your imputation cycle. 

# Save the "Listwise_m_Reg_Imputation" as the new dataset
d_ListWiseRegImp <- complete(Listwise_m_Reg_Imputation)

# Run an GLM using the d_ListWiseRegImp to see how the model fits the data (how the model best represents the relationship oberved in the data).
m_Reg_Imp <- lm(bdi ~ traitanx + bfagree, data = d_ListWiseRegImp)
summary(m_Reg_Imp)

# Combine and compare the coefficients
(coeffs <- rbind(coeffs, coef(m_Reg_Imp)))

# Combine and compare the SEs
(SEs = rbind(SEs, summary(m_Reg_Imp)$coefficients[,"Std. Error"]))

# Combine and compare the p.values
(pvals <- rbind(pvals, summary(m_Reg_Imp)$coefficients[,"Pr(>|t|)"]))
```

------------------------------------------------------------------------

##### Stochastic Regression Imputation

mice: "norm.nob" and m = 1 is Stochastic Regression Imputation

```{r}
# Conduct Stochastic Imputation and add results to 
Listwise_m_Sto_Imputation <- mice(listwise_15, method = "norm.nob", m = 1)
d_ListWiseStoImp <- complete(Listwise_m_Sto_Imputation)
m_Sto_Imp <- lm(bdi ~ traitanx + bfagree, data = d_ListWiseStoImp)
summary(m_Sto_Imp)
confint(m_Sto_Imp)

#rbind and compare with the rest of "Coeffs", "SEs", and "pvals"
(coeffs <- rbind(coeffs, coef(m_Sto_Imp)))
(SEs <- rbind(SEs, summary(m_Sto_Imp)$coefficients[,"Std. Error"]))
(pvals <- rbind(pvals, summary(m_Sto_Imp)$coefficients[,"Pr(>|t|)"]))
```

##### Multiple Imputation

```{r}
Listwise_m_Mul_Imputation <- mice(listwise_15, method = "norm.nob", m = 10, printFlag=FALSE)
d_ListWiseMulImp <- complete(Listwise_m_Mul_Imputation)
m_Mul_Imp <- lm(bdi ~ traitanx + bfagree, data = d_ListWiseMulImp)
summary(m_Mul_Imp)
confint(m_Mul_Imp)

#rbind and compare with the rest of "Coeffs", "SEs", and "pvals"
(coeffs <- rbind(coeffs, coef(m_Mul_Imp)))
(SEs <- rbind(SEs, summary(m_Mul_Imp)$coefficients[,"Std. Error"]))
(pvals <- rbind(pvals, summary(m_Mul_Imp)$coefficients[,"Pr(>|t|)"]))
```

##### Expectation-Maximization

```{r}
library(missMethods)
d_EM <- impute_EM(listwise_15)
m_EM_Imp <- lm(bdi ~ traitanx + bfagree, data = d_EM)
summary(m_EM_Imp)
confint(m_EM_Imp)

#rbind and compare coefficients, SEs and pvals
(coeffs <- rbind(coeffs, coef(m_EM_Imp)))
(SEs = rbind(SEs, summary(m_EM_Imp)$coefficients[,"Std. Error"]))
(pvals <- rbind(pvals, summary(m_EM_Imp)$coefficients[,"Pr(>|t|)"]))
```

\

#### 
