---
title: "Exercise03-Missing_Data"
author: "Ken Suzuki"
date: "2023-10-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A researcher is interested in predicting depression from trait anxiety and agreeableness. The dataset is called epi.bfi and resides within the psychTools package.

Depression was measured with the Beck Depression Inventory (bdi), trait anxiety was measured with the State-Trait Anxiety Inventory (traitanx), and agreeableness was measured with the Big 5 Inventory (bfagree). Use α = .05 for any null hypothesis testing.

```{r}
#Load required libraries
library(psychTools)
library(missMethods)

# Load and check the dataset
d <- epi.bfi
str(d)
head(d)
nrow(d) #This is to find out the number of rows (data pints) in the dataset

# Run a regular model without removing the data
m <- lm()


```

```         
Variable Descriptions
epiE: EPI Extraversion
epiS: EPI Sociability (a subset of Extraversion items
epiImp: EPI Impulsivity (a subset of Extraversion items
epilie: EPI Lie scale
epiNeur: EPI neuroticism
bfagree: Big 5 inventory (from the IPIP) measure of Agreeableness
bfcon: Big 5 Conscientiousness
bfext: Big 5 Extraversion
bfneur: Big 5 Neuroticism
bfopen: Big 5 Openness
bdi: Beck Depression scale
traitanx: Trait Anxiety
stateanx: State Anxiety
```

#### 1) Use the delete_MCAR function from the missMethods package to randomly remove 15% of cases from each variable. Save this dataset with a new name.

#### 2) Determine if the missing data can be classified as 'missing completely at random' (you should be able to predict the answer from Q1).

#### 3) Run a general linear model predicting depression from trait anxiety and agreeableness using each of the following strategies:  

##### a. Complete Data 

##### b. Listwise Deletion 

##### c. Regression Imputation 

##### d. Stochastic Regression Imputation 

##### e. Expectation-Maximization 

##### f. Multiple Imputation

#### 4) Explore the unstandardized regression coefficients resulting from each strategy in Q3. Are there any noticeable differences between strategies?

#### 5) Explore the standard errors for the coefficients resulting from each strategy in Q3. Are there any noticeable differences between strategies? (We could/should have also looked at the p-values, standardized effect sizes, etc.)
